%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Associate Professor, Department of Computer Science}
    {University of Girona}
    {Girona, Spain}
    {Sep. 2024 - now}
    {
    \begin{cvitems}
    \item {Led labs instructing students on functional and object-oriented programming paradigms.}
    \item {Led labs instructing students on imperative programming paradigms.}
    \item{Created, expanded and corrected deliverable projects.}
    \item{Provided support and assistance to students.}
    \item {
      \textbf{
        Scala \textbar \
        C++ \textbar \
        Python \textbar \
        \LaTeX
      }
    }
    \end{cvitems}
  }
  \cventry
    {Associate Professor, Department of Computer Science}
    {} % Organization EMPTY
    {} % Location EMPTY
    {Gen. 2023 - Jun. 2023} % Date(s)
    {
    \begin{cvitems}
    \item {Led labs instructing students on functional and logic programming paradigms.}
    \item{Assisted in the development of exams and supervised their administration.}
    \item{Created, expanded, and corrected deliverable projects.}
    \item{Provided support and assistance to students.}
    \item {
      \textbf{
        Haskell \textbar \
        Prolog \textbar \
        \LaTeX
      }
    }
    \end{cvitems}
    \vspace{0.25cm}
 	  }


  \cventry
  {Data Scientist} % Job title
  {Citibeats} % Organization
  {Barcelona, Spain} % Location
  {Sep. 2023 - Mar. 2024} % Date(s)
  {
  \begin{cvitems}
    \item {Developed and deployed topic modeling pipelines with LLMs like BERT improving topic relevance recomendations.}
    \item {Worked on anomaly detection and forecasting projects using statistical methods and deep learning architectures
      such as RNNs and LSTM.}
    \item {Provided technical support for legacy projects, enhancing model performance through improved metrics and bug fixes.}
    \item {Increased the explainability of legacy models by utilizing clustering techniques and model-based feature extraction.}
    \item {Developed private Python libraries and web-hook services, deploying models in private repositories.}
    \item {Conducted rapid experiments, thoroughly documenting processes for reproducibility.}
    \item {
      \textbf{
        Python \textbar \
        PyTorch \textbar \
        Sklearn \textbar \
        Hugging Face \textbar \
        FastAPI \textbar \
        Docker \textbar \
        AWS \textbar \
        Google Colab \textbar \
        Git \textbar \
        MLflow
      }
    }
  \end{cvitems}
  }

    %---------------------------------------------------------

    \cventry
    {Computer Vision Research} % Job title
    {Accenture SL} % Organization
    {Girona, Spain} % Location
    {Dec. 2022 - Aug. 2023} % Date(s)
    {
    \begin{cvitems}
    \item {Developed and open-sourced a CAD platform using CNNs for melanoma detection image based.}
    \item {
      \textbf{
        Python \textbar \
        PyTorch \textbar \
        Sklearn \textbar \
        Pandas \textbar \
        Albumentations \textbar \
        Docker \textbar \
        Svelte \textbar \
        Git \textbar \
        Markdown \
     }
    }
    \end{cvitems}
    }

      %---------------------------------------------------------
      \cventry
      {Data Engineer} % Job title
      {Nexus Geographics} % Organization
      {Girona, Spain} % Location
      {Sep. 2021 - Sep. 2022} % Date(s)
      {
        \begin{cvitems}
        \item {Contributed to the development of a concurrent framework for data capture, increasing efficiency by 200\%.}
        \item {Created and maintained API micro-services, ensuring data consistency across multiple SQL and NoSQL databases.}
        \item {Designed and developed interactive web applications to visualize
          on-demand and streaming data.}
        \item {Trained new team members on key technologies, reducing onboarding time by 30\%.}
        \item {
          \textbf{
            Java \textbar \
            Python \textbar \
            Scala \textbar \
            PySpark \textbar \
            Shell \textbar \
            Git \textbar \
            CI/CD \textbar \
            Docker \textbar \
            Kafka \textbar \
            SQL \textbar \
            Flask \textbar \
            Angular \textbar \
            Markdown
         }
        }
        \end{cvitems}
      }


      %---------------------------------------------------------
      \cventry
      {Software Engineer} % Job title
      {NexTReT} % Organization
      {Girona, Spain} % Location
      {Abr. 2020 - Sep. 2021} % Date(s)
      {
        \begin{cvitems}
        \item {Designed and developed a wide range of Restful APIs.}
        \item {Built interactive web applications for healthcare, streamlining hospital operations and reducing manual entry by 150\%.}
        \item {
          \textbf{
            Java \textbar \
            Python \textbar \
            JS \textbar \
            Shell \textbar \
            Git \textbar \
            CI/CD \textbar \
            SQL \textbar \
            Spring Boot \textbar \
            Angular
         }
        }
        \end{cvitems}
      }

  \end{cventries}
